\documentclass[11pt,]{article}
\usepackage[margin=1in]{geometry}
\newcommand*{\authorfont}{\fontfamily{phv}\selectfont}
\usepackage[]{mathpazo}
\usepackage{abstract}
\renewcommand{\abstractname}{}    % clear the title
\renewcommand{\absnamepos}{empty} % originally center
\newcommand{\blankline}{\quad\pagebreak[2]}

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}} 
\usepackage{longtable,booktabs}

\usepackage{parskip}
\usepackage{titlesec}
\titlespacing\section{0pt}{12pt plus 4pt minus 2pt}{6pt plus 2pt minus 2pt}
\titlespacing\subsection{0pt}{12pt plus 4pt minus 2pt}{6pt plus 2pt minus 2pt}

\titleformat*{\subsubsection}{\normalsize\itshape}

\usepackage{titling}
\setlength{\droptitle}{-.25cm}

%\setlength{\parindent}{0pt}
%\setlength{\parskip}{6pt plus 2pt minus 1pt}
%\setlength{\emergencystretch}{3em}  % prevent overfull lines 

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}

\usepackage{fancyhdr}
\pagestyle{fancy}
\usepackage{lastpage}
\renewcommand{\headrulewidth}{0.3pt}
\renewcommand{\footrulewidth}{0.0pt} 
\lhead{}
\chead{}
\rhead{\footnotesize PS 140A: Congress (Section) -- Fall 2018}
\lfoot{}
\cfoot{\small \thepage/\pageref*{LastPage}}
\rfoot{}

\fancypagestyle{firststyle}
{
\renewcommand{\headrulewidth}{0pt}%
   \fancyhf{}
   \fancyfoot[C]{\small \thepage/\pageref*{LastPage}}
}

%\def\labelitemi{--}
%\usepackage{enumitem}
%\setitemize[0]{leftmargin=25pt}
%\setenumerate[0]{leftmargin=25pt}




\makeatletter
\@ifpackageloaded{hyperref}{}{%
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
}
\@ifpackageloaded{color}{
    \PassOptionsToPackage{usenames,dvipsnames}{color}
}{%
    \usepackage[usenames,dvipsnames]{color}
}
\makeatother
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={ ()},
             pdfkeywords = {},  
            pdftitle={PS 140A: Congress (Section)},
            colorlinks=true,
            citecolor=blue,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls


\setcounter{secnumdepth}{0}





\usepackage{setspace}

\title{PS 140A: Congress (Section)}
\author{Derek E. Holliday}
\date{Fall 2018}


\begin{document}  

		\maketitle
		
	
		\thispagestyle{firststyle}

%	\thispagestyle{empty}


	\noindent \begin{tabular*}{\textwidth}{ @{\extracolsep{\fill}} lr @{\extracolsep{\fill}}}


E-mail: \texttt{\href{mailto:deholliday@g.ucla.edu}{\nolinkurl{deholliday@g.ucla.edu}}} & Web: \href{http://github.com/deholliday}{\tt github.com/deholliday}\\
Office Hours: T/TR 2:30-3:30 p.m.  &  Class Hours: F 3-3:50 p.m. (2D), 4-4:50 (2E), 5-5:50 (2F)\\
Office: 3288 Bunche Hall  & Class Room: 3156 Bunche Hall\\
	&  \\
	\hline
	\end{tabular*}
	
\vspace{2mm}
	


\subsection{Section Description}\label{section-description}

The purpose of section is to engage with the literature and make sure
that students have a clear understanding of the reading and concepts
covered in class, with an emphasis on the readings assigned for section.
We will discuss not only the reading, but also expand upon the
relationship that the readings and lectures share with our own knowldge
of Congress and politics.

\subsection{Participation}\label{participation}

Participation accounts for 10 percent of your overall grade. Students
are expected to finish all assigned readings and be prepared to actively
participate in discussion. Just being present is not enough.
Participation is comprised of multiple components and active engagement
and questins are highly encouraged. Should lack of participation become
an issue, I reserve the right to cold call or eventually give pop
quizzes in section that will be used to determine participation credit.

\subsection{Attendance Policy}\label{attendance-policy}

Attendance at each discussion section is \textbf{mandatory}. Excused
absences will be granted for medically documented emergencies or
illnesses (this requires a doctor's letter) or a note from a UCLA
administrator explaining your extenuating circumstances. Absences are
unexcused for all other reasons. Everyone gets on free unexcused absence
from discussion section. After your free unexcused absence, every
additional unexcused absence thatyou miss will lower your final letter
grade in this course by half a letter grade.

In addition to being present, it is also important that you are on time.
Anyone who is more than 10 minutes late will be marked as absent.

\subsection{Rules and Guidelines}\label{rules-and-guidelines}

\begin{itemize}
\item
  \textbf{Grievance policy-} You have \textbf{one week} to place in
  writing, via email, a request to re-grade your assignment. All grade
  requests mustbe sent to professor Tausanovitch and myself. To submit a
  re-grade request, you will need to write up a one page outline
  explaining which portions of your exam you believe should be
  re-graded. In addition to submitting a request, you must also set up a
  time to return your assignment to me so that I can take your request
  into consideration. When submitting a re-grade request, be aware of
  that fact that your grade may go up or down. Re-grades will only be
  considered for the midterm. \textbf{Only emailed grade requests will
  be considered.}
\item
  \textbf{Office Hours-} Office hours will be held Tuesdays and
  Thursdays from 2:30 to 3:30 p.m. in the TA room (Bunche 3288), If
  office hours conflict with your course schedule, feel free to email me
  and setee up an appointment on a different day.
\item
  \textbf{Electronics-} You are welcome to use your laptops in class so
  long as they do not serve as a distraction. This means no Facebook,
  iChat, Gchat, Twitter, ESPN, etc. Allowing the use of computers is
  meant for note taking and to reference previous notes. If it becomes a
  problem I will ask you to put your computers away. I also ask that you
  place your phones away and on silent during class in order to minimize
  disruptions.
\end{itemize}

\subsection{Academic Honesty}\label{academic-honesty}

Your work should consist of your own ideas and your own words.
Quotations and ideas used from other authors must be properly cited If
you are unfamiliar with the University's policy on academic dishonesty
and associated penalties, see \url{http://www.deanofstudents.ucla.edu}.
Plagiarism or any other form of academic dishonesty will be reported to
the Dean.

\subsection{Final Remarks}\label{final-remarks}

I reserve the right to make changes to the section syllabus at any point
in the quarter should I feel it that it would better enhance our
discussion section. Also, I cannot stress enough the importance of
communicating with me should problems arise at the time that they
happen. It is better to address problems early than wait for someone to
come to you.




\end{document}

\makeatletter
\def\@maketitle{%
  \newpage
%  \null
%  \vskip 2em%
%  \begin{center}%
  \let \footnote \thanks
    {\fontsize{18}{20}\selectfont\raggedright  \setlength{\parindent}{0pt} \@title \par}%
}
%\fi
\makeatother